\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-08 paper/main.tex
first pass on abstract
changing author ordering
title change as per Saikat's recommendation
minor changes to abstract

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{\tname: A Database of Bugs in Deep Learning Libraries to
  Enable the Evaluation of Testing Techniques}

@@

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLL), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of techniques have been recently proposed to
  find those bugs, but the lack of curated set of reproducible bugs
  hinders credible evaluation of those techniques. We present \tname,
  a database of curated reproducible bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{\tname: A Database of Reproducible Bugs in Deep
  Learning Libraries to Enable Systematic Evaluation of Testing
  Techniques}

@@

\author{Benjamin Wu}
\affiliation{%
 \institution{?}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{?}}
\email{?}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of techniques have been recently proposed to
  find those bugs, but the lack of a curated set of reproducible bugs
  in DLLs hinders credible evaluation of testing techniques. We present \tname,
  a database of curated reproducible bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}
